%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,10.9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust marginshttps://www.overleaf.com/project/6545a79dbd07bb45b3c33e83
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small#4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small #3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
  \textbf{\Huge \scshape Jesus Mancilla} \\
  \small
  \faMobile \hspace{.5pt} \href{tel:16503914301}{+1 650 391 4301}
  $|$
  \faAt \hspace{.5pt} \href{mailto:jesus@jgmancilla.com}{jesus@jgmancilla.com}
  $|$
  \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/jegama}{LinkedIn.com/in/jegama}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/jegama}{GitHub.com/jegama}
  $|$
  \faGlobe \hspace{.5pt} \href{https://www.jgmancilla.com}{jgmancilla.com}
\end{center}



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Meta}{}
      {Senior Quant User Experience Researcher}{Jan 2024 - Present}
        \resumeItemListStart
        % The presentation is about a new algorithm for analyzing open-ended responses. The current solution, Qualtrics, relies on word counts and frequency analysis, which can be limited in understanding the meaning of words. The new algorithm uses clustering analysis, multi-agent chain-of-reasoning, human-in-the-loop feedback, and few-shot learning to improve semantic understanding, pattern discovery, and robustness to noise. It can generate labels autonomously and adapt to diverse domains and tasks through expert feedback. The algorithm consists of five steps: clustering similar responses together, creating multiple labels per cluster, consolidating topics and themes, giving feedback to the model, and classifying responses using a few-shot prompt. The output includes visualizing the prevalence of key concepts in the data, such as themes, sub-themes, and topics.
            \resumeItem{Developed and implemented a hybrid machine learning classifier for open-ended responses, utilizing clustering analysis, multi-agent chain-of-reasoning, human-in-the-loop feedback, and few-shot learning, significantly reducing analysis time.}
            \resumeItem{Led the development of Python-based analytical tools to streamline survey data analysis, enabling efficient processing and supporting fellow researchers across multiple projects.}
            \resumeItem{Merged behavioral data from editor logs and in-app surveys, employing data science and machine learning methodologies to produce comprehensive, data-driven insights.}
            \resumeItem{Conducted longitudinal research on a novel machine learning model, overseeing the design and execution of bi-weekly surveys and identifying critical performance metrics for a product with over 500 million monthly active users.}
        \resumeItemListEnd
    

    \resumeSubheading
      {Roku Inc.}{}
      {Senior User Experience Researcher}{Jan 2021 - Nov 2023}
        \resumeItemListStart
            \resumeItem{Spearheaded the creation of an AI-powered indexed database of Roku's UX and CI research, enhancing data accessibility and leveraging AI techniques to improve search capabilities across the organization.}
            \resumeItem{Developed the Modular Survey Analysis System, integrating machine learning algorithms for generating detailed reports on survey data, including statistical analysis and NLP-based categorization of open-ended responses.}
            \resumeItem{Led quantitative and qualitative research on physical devices, deriving insights through behavioral log analysis from over 70 million devices to inform product development.}
            % \resumeItem{Executed comprehensive UX research on Roku's Customer Support site and call center software, utilizing data-driven methodologies to enhance user experience and optimize support processes.}
        \resumeItemListEnd

    \resumeSubheading
      {Walmart Global Tech}{}
      {Senior User Experience Researcher}{Aug 2019 - Nov 2020}
        \resumeItemListStart
            \resumeItem {Orchestrated comprehensive data analytics projects for Sam's Club's mobile app using Tableau, establishing key performance metrics to guide strategic enhancements.}
            \resumeItem {Pioneered a data-centric approach, integrating user interaction data with business metrics to inform and transform the user experience.}
            \resumeItem{Presented synthesized research findings to a diverse group of stakeholders, including product managers, designers, and executives, influencing the user experience strategy and design decisions.}
        \resumeItemListEnd

    \resumeSubheading
      {Scrapworks inc.}{}
      {Data Scientist}{Sep 2017 - Aug 2019}
        \resumeItemListStart
            \resumeItem {Spearheaded a successful deep learning project that accurately forecasted commodities futures, yielding a 60\% reduction in prediction error.}
            \resumeItem {Initiated an NLP-based merchandise classification project, contributing to a patent application and aiding strategic business decision-making.}
            \resumeItem{Created an interactive dashboard to visualize and filter 20 years of sales data, driving a 30\% sales growth.}
        \resumeItemListEnd

    \resumeSubheading
      {Suggestic}{}
      {Senior User Experience Researcher}{Dec 2016 - Sep 2017}
        \resumeItemListStart
            \resumeItem {Led the transition from a conversational to a graphical interface, utilizing data insights to guide design decisions, significantly enhancing user engagement and app functionality.}
            \resumeItem {Executed data-driven testing and analysis for new app features, ensuring optimal integration and alignment with user needs and business objectives.}
            \resumeItem{Designed and developed advanced app prototypes, leveraging analytics to inform rapid iterations and feature enhancements.}
        \resumeItemListEnd

    \resumeSubheading
      {Stanford University}{}
      {User Experience Researcher}{May 2016 - Nov 2016}
        \resumeItemListStart
            \resumeItem {Conducted pioneering research on stress detection using machine learning algorithms, collecting and analyzing over 150 hours of car, biometric, and video data.}
            \resumeItem {Contributed to the development of algorithms with 90\% accuracy in stress detection.}
            \resumeItem{Authored and contributed to research papers on automotive UI and pedestrian interactions, enhancing the academic discourse in UX design.}
        \resumeItemListEnd

    \resumeSubheading
      {ITAM}{}
      {User Experience Researcher}{Aug 2014 - May 2016}
        \resumeItemListStart
            \resumeItem {Created custom data visualizations and analyzed psychophysiological signals, identifying user behavior patterns using machine learning techniques.}
            \resumeItem{Crafted personalized user experience solutions for interactive technologies, spanning wearable, mobile, and web platforms.}
            \resumeItem {Conducted comprehensive usability testing at various development stages, significantly improving user interaction and satisfaction.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

  %----------- MACHINE LEARNING PROJECTS -----------

\section{MACHINE LEARNING PROJECTS}
\vspace{2pt}
\resumeSubHeadingListStart
  \small{\item{
      
      \textbf{Research Librarian Project:}{ Developed an AI-powered index for UX and CI research, enhancing data retrieval  \\ \hspace{23pt} and user experience with an innovative indexing algorithm. (\href{https://www.jgmancilla.com/research-librarian}{Link})} 
      
      \textbf{Modular Survey Analysis System:}{ Created a machine learning-based report generator for survey analysis,  \\ \hspace{23pt} integrating context-aware logic and autonomous clustering algorithms, improving efficiency and resource  \\ \hspace{23pt} utilization. (\href{https://www.jgmancilla.com/modular-survey-report-generator}{Link})} 
      
      \textbf{Customer Support Bot:}{ Enhanced customer support with an autonomous agent using advanced ML technology, \\ \hspace{23pt} including embeddings and LLMs, improving self-service and customer satisfaction. (\href{https://www.jgmancilla.com/customer-support-bot-project}{Link})} 
      
  }}
\resumeSubHeadingListEnd

  %----------- PUBLICATIONS -----------

\section{Publications}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        {Baltodano, Sonia, Jesus Garcia-Mancilla, and Wendy Ju. "Eliciting Driver Stress Using Naturalistic Driving Scenarios on Real Roads." In Proceedings of the 10th International Conference on Automotive User Interfaces and Interactive Vehicular Applications, pp. 298-309. ACM, 2018.} 

        {Currano, Rebecca, So Yeon Park, Lawrence Domingo, Jesus Garcia-Mancilla, Pedro C. Santana-Mancilla, Victor M. Gonzalez, and Wendy Ju. "¡Vamos!: Observations of Pedestrian Interactions with Driverless Cars in Mexico." In Proceedings of the 10th International Conference on Automotive User Interfaces and Interactive Vehicular Applications, pp. 210-220. ACM, 2018.} 

        {J. Garcia-Mancilla, J. E. Ramirez-Marquez, C. Lipizzi, G. T. Vesonder, and V. M. Gonzalez, “Characterizing negative sentiments in at-risk populations via crowd computing: a computational social science approach,” International Journal of Data Science and Analytics, Jun. 2018.} 

        {Garcia-Mancilla J., Martinez V.R., Gonzalez V.M., Fajardo A.F. (2016) Social Influence and Emotional State While Shopping. In: Nah FH., Tan CH. (eds) HCI in Business, Government, and Organizations: eCommerce and Innovation. HCIBGO 2016. Lecture Notes in Computer Science, vol 9751. Springer, Cham.} 

        {Garcia-Mancilla J., Gonzalez V.M. (2016) Stress Quantification Using a Wearable Device for Daily Feedback to Improve Stress Management. In: Zheng X., Zeng D., Chen H., Leischow S. (eds) Smart Health. Lecture Notes in Computer Science, vol 9545. Springer, Cham.} 

        {L. Ferrer, J. Garcia-Mancilla, V. M. Gonzalez, S. Bermudez, P. Bleier and C. Prieto, "Using augmented reality in urban context: Georeferenced system for business localization using Google Glass," 2015 IEEE First International Smart Cities Conference (ISC2), Guadalajara, 2015, pp. 1-6. doi: 10.1109/ISC2.2015.7366157.} 

        {González V.M., García J., Muro B. (2015) Searching for Information: Comparing Text vs. Visual Search with Newspapers Websites. In: Yamamoto S. (eds) Human Interface and the Management of Information. Information and Knowledge Design. HIMI 2015. Lecture Notes in Computer Science, vol 9172. Springer, Cham.} 

        {Montes R., Garcia-Mancilla J. (2015), Programas psicoeducativos para el autocontrol de la diabetes de corte cognitivo-conductual In G. Solano, A. Del Castillo, R. M. E. Guzman, M. Garcia, A. Romero (Ed.), Diabetes y Educacion, de la teoria a la practica (119-146). Ciudad de Mexico: Planeacion y Servicio Editorial S.A.} 

        {Garcia-Mancilla J., Montes-Delgado R., Santana-Mancilla P. Quality of Life (QoL) and self-efficacy on elderly with diabetes mellitus type 2: Study in the Mexican State of Colima. Rendez-Vous 2012, Thunder Bay, Canada, Octubre 2012.} 

        {Montes R., Garcia-Mancilla J., Oropeza-Tena R. Self-control techniques for the right management of diabetes mellitus type 2 (DM2) in adults. Rendez-Vous 2012, Thunder Bay, Canada, Octubre 2012.} 

        {Garcia-Mancilla, J., Rodriguez-Morrill, E. I. y Velasco-Alcazar, C. C. (2011). Análisis de contenidos sobre adultos mayores en las currículas de la Universidad de Colima. Universidad de Colima: Colima, México.} 
    }}
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Programming Languages:}{ Advanced proficiency in Python, R, SQL}
                
        \textbf{Machine Learning:}{ Expertise in machine learning, deep learning, NLP, LLMs, RNNs, transformers, prompt engineering}

        \textbf{Data Analysis:}{ Statistical analysis, data visualization, predictive modeling, trend analysis, KPI development}

        \textbf{Databases:}{ Experience with Vector Databases, building automation pipelines, data processing, workflow optimization}

        \textbf{Languages:}{ Fluent in Spanish and English}

        \textbf{Tools and Frameworks:}{ TensorFlow, PyTorch, Scikit-learn, Pandas, NumPy}
        
    }}
  \resumeSubHeadingListEnd

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Instituto Technologico Autonomo de Mexico}{}
      {Master of Science, Computer Science}{2014 - 2016}

    \resumeEducationHeading
      {Universidad de Colima}{}
      {Bachelor’s Degree, Psychology}{2009 - 2013}
    
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}